The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-10 paper/ms.tex
initialize new eclipsing binary section

\subsubsection{Eclipsing Binaries}
\label{ebs}
We detect some eclipsing binaries \textcolor{red}{Ben - finish this.}

>>>>

\subsubsection{Binaries}
\label{ebs}

We detect BD+47~2825 as a new eclipsing binary system, and recover light curves for the previously-known eclipsing binaries HD~186994, V2083~Cyg, and V380~Cyg. The known binary system HD~189684 is newly identified as showing ellipsoidal variability, but does not show evidence of eclipses. \textcolor{red}{Finish this section?}
